\vspace{-0.8in}Brief Announcement: A Family of Leaderless Generalized-Consensus Algorithms

### 2016-02-12 podc16/paper2.tex

A dependency-set algorithm exposes the input interface $\opn{announce}_p\left( c \right)$, to announce a command $c$, the output interface $\opn{suggest}_p \left( c,\mathcal{D}\right)$, to suggest a set of dependencies $\mathcal{D}$ for $c$, and an input interface $\opn{commit}\left( c,\mathcal{D} \right)$ (meant to observe the map-agreement sub-algorithm), where $p\in P$ is the process executing the call.
Moreover, a dependency-set algorithm must ensure that:
\begin{itemize}[noitemsep,nolistsep]
    \item[-] Safety: (a), for any suggestion $\opn{suggest}_p \left( c,\mathcal{D}\right)$, every command in $\{c\}\cup \mathcal{D}$ must have been announced before; (b), for any two suggestions $\opn{suggest}_p \left( c_1,\mathcal{D}_1\right)$ and $\opn{suggest}_q \left( c_2,\mathcal{D}_2\right)$, if $c_1$ and $c_2$ do not commute then either $c_1\in \mathcal{D}_2$ or $c_2 \in \mathcal{D}_1$.
%    \item If $c$ was announced by $p$, then eventually a dependency set is suggested for $c$ to $p$.
    \item[-] Liveness: (a) If a suggestion $\opn{suggest}_p\left( c \right)$ was made, then eventually a suggestion $\opn{suggest}\left( c,\mathcal{D} \right)_p$ is made, and (b), if a suggestion $\opn{suggest}_p(c,\mathcal{D})$ has been made and no input $\opn{commit}_q\left( c,\mathcal{D'} \right)$ is observed, then eventually a new suggestion $\opn{suggest}_r\left( c,\mathcal{D''} \right)$ for $r\neq p$ is made.
\end{itemize}
\vspace{5cm}

>>>>

A dependency-set algorithm exposes the input interface $\opn{announce}_p\left( c \right)$, to announce a command $c$, the output interface $\opn{suggest}_p \left( c,\mathcal{D}\right)$, to suggest a set of dependencies $\mathcal{D}$ for $c$, and an input interface $\opn{commit}\left( c,\mathcal{D} \right)$ (meant to observe the map-agreement sub-algorithm), where $p\in P$ is the process executing the call.
Moreover, a dependency-set algorithm must ensure that:
\begin{itemize}[noitemsep,nolistsep]
    \item[-] Safety: (a), for any suggestion $\opn{suggest}_p \left( c,\mathcal{D}\right)$, every command in $\{c\}\cup \mathcal{D}$ must have been announced before; (b), for any two suggestions $\opn{suggest}_p \left( c_1,\mathcal{D}_1\right)$ and $\opn{suggest}_q \left( c_2,\mathcal{D}_2\right)$, if $c_1$ and $c_2$ do not commute then either $c_1\in \mathcal{D}_2$ or $c_2 \in \mathcal{D}_1$.
%    \item If $c$ was announced by $p$, then eventually a dependency set is suggested for $c$ to $p$.
    \item[-] Liveness: (a) If a suggestion $\opn{suggest}_p\left( c \right)$ was made, then eventually a suggestion $\opn{suggest}\left( c,\mathcal{D} \right)_p$ is made, and (b), if a suggestion $\opn{suggest}_p(c,\mathcal{D})$ has been made and no input $\opn{commit}_q\left( c,\mathcal{D'} \right)$ is observed, then eventually a new suggestion $\opn{suggest}_r\left( c,\mathcal{D''} \right)$ for $r\neq p$ is made.
\end{itemize}

An example of implementation of such an algorithm is depicted by the pseudocode of Figures~\ref{fig:deps-set-algo1} and~\ref{fig:deps-set-algo2}. Due to space constraints, our example focuses on satisfying the safety property only. The main idea is the following: a process $p$ announcing a command $c$ broadcasts $c$ to all the processes, and it suggests the dependency-set $deps_p[c]$ for $c$ as the union of the sets $\mathcal{D}$ that it receives as replies from a quorum of $\mathcal{Q}$ processes; on the other hand, a process that receives an announcement for $c$, computes its reply $\mathcal{D}$ for $c$ as the set of commands $d$ that it received so far, and such that $c$ and $d$ do not commute. The choice of the value of $\mathcal{Q}$ must be such that the intersection of any two quorums is not empty. About correctness, we can easily prove that such an implementation satisfies the safety property by noticing that:  any process $p$ inserts a command $d$ in a dependency-set $\mathcal{D}$ that $p$ sent as a reply for a command $c$, only if $p$ previously received $d$. Therefore, every command suggested in a dependency-set must have been announced before. Further, since a process can suggest a set of dependencies $deps_p[c]$ for a command $c$ after it has received a reply for $c$ from at least a quorum of processes, and thanks to the requirement that we enforced on the intersection of quorums, we can conclude that for any two suggestions $\opn{suggest}_p \left( c_1,deps_p[c_1]\right)$ and $\opn{suggest}_q \left( c_2,deps_q[c_2]\right)$,  if $c_1$ and $c_2$ do not commute then either $c_1\in deps_q[c_2]$ or $c_2 \in deps_p[c_1]$.
